---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# b2lpuumala
Lauren Puumala  
2023-11-10  
<!-- badges: start -->
<!-- badges: end -->

## Description
This package contains a function called `count_obs` that can be used to count the number of observations of a categorical variable or combinations of categorical variables in a data frame. It returns the results as a tibble. Relevant documentation, tests, and examples for this function are included in this package as well.  
  
**Function specifications:**    
- Parameters:  
  - `data`: the data frame  
  - `group_vars`: categorical variables in `data` to be used for grouping. Grouping variables must belong to one of the following classes: character, factor, or date.  
- Result: a tibble tabulating the number of observations of the specified categorical grouping variable(s) in `data`.  
  
    
**Files and folders in this repo:**  
- **.gitignore:** text file to specify which files should not be tracked by Git  
- **.Rbuildignore:** exclude files from being put in the package   
- **b2lpuumala.Rproj:** Rstudio project file for this assignment  
- **DESCRIPTION:** metadata about the package  
- **LICENSE:** copyright info  
- **LICESE.md:** .md file containing MIT license details  
- **man:** folder containing function documentation  
- **NAMESPACE:** declares which functions this package exports for external use and which functions it imports from external packages  
- **NEWS.md:** news file with development notes  
- **R:** folder containing R files with function definitions  
- **README.Rmd:** this README file (R Markdown version)  
- **README.md:** this README file (GitHub Markdown version)  
- **tests:** folder containing function tests   
  
  
## Demonstrated Usage  
```{r error = TRUE}
library(b2lpuumala)

#CORRECT USAGE
#Using the vancouver_trees dataset from datateachr
#One grouping variable
count_obs(datateachr::vancouver_trees, "neighbourhood_name")

#Multiple grouping variables
count_obs(datateachr::vancouver_trees, c("neighbourhood_name", "genus_name", "species_name"))

#INCORRECT USAGE  
#Error is thrown when group_vars contains at least one variable that is the wrong class. See examples below.
count_obs(datateachr::vancouver_trees, "diameter")

count_obs(datateachr::vancouver_trees, c("neighbourhood_name", "diameter"))
```

## Installation

You can install the development version of b2lpuumala from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("stat545ubc-2023/b2lpuumala", ref = "0.1.0")
```
