---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# b2lpuumala
Lauren Puumala  
2023-11-10  
<!-- badges: start -->
<!-- badges: end -->

## Description
This package contains a function called `count_obs` that can be used to count the number of observations of a categorical variable or combinations of categorical variables in a data frame. It returns the results as a tibble. Relevant documentation, tests, and examples for this function are included in this package as well.  
  
**Function specifications:**    
- Parameters:  
  - `data`: the data frame  
  - `group_vars`: categorical variables in `data` to be used for grouping. Grouping variables must belong to one of the following classes: character, factor, or date.  
- Result: a tibble tabulating the number of observations of the specified categorical grouping variable(s) in `data`.  

**Files and folders in this repo**  
File/Folder Name | Description
-----------------|------------
README.Rmd | This README file (R Markdown version)
README.md | This README file (GitHub Markdown version)
.gitignore | Text file to specify which files should not be tracked by Git
.Rbuildignore | Exclude files from being put in the package
.Rhistory | History of executed code
b2lpuumala.Rproj | Rstudio project file for this assignment
DESCRIPTION | Metadata about the package
man | Folder containing function documentation
NAMESPACE | Declares which functions this package exports for external use and which functions it imports from external packages
R | Folder containing R files with function definitions
ADD TEST FILES | update later!


## Demonstrated Usage  
```{r error = TRUE}
#Using the vancouver_trees dataset from datateachr
#One grouping variable
count_obs(vancouver_trees, "neighbourhood_name")

#Multiple grouping variables
count_obs(vancouver_trees, c("neighbourhood_name", "genus_name", "species_name"))

#Error is thrown when group_vars contains at least one variable that is the wrong class
count_obs(vancouver_trees, "diameter")
count_obs(vancouver_trees, c("neighbourhood_name", "diameter"))
```

## Installation

You can install the development version of b2lpuumala from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("stat545ubc-2023/b2lpuumala")
```
